\paragraph{Triangulation}
Triangulation is used on a number of distance measurements to a number of reference points. 
Typically the distance is measured using the signal strength between tag and reader or the time of arrival of the signal.
A model is then used to map the distance measurements to a 2D or 3D position of the tag.\cite{rfidreview}

\paragraph{SpotON}
An implementation of triangulation is the SpotON system\cite{spoton}.
SpotON uses several basestation that are all connected to a central server.
The server aggregates the received positions, triangulates the data and sends the resulting position to clients. \cite{spoton}

The algorithm used for triangulating the positions is a hillclimbing algorithm as presented in section 3.3.1 of \citet{spoton}.
The algorithm starts from a arbitrary position and searches for the position by calculating the theoretical signal strengths for adjacent positions.
These theoretical signal strengths are calculated with a modeled formula for each basestation based on empirical data.
The theoretical signal strengths are then compared to the observed signal strengths, and the point with the smallest error is used as the next point of origin.
The process is repeated until the point does not move \cite{spoton}.

\paragraph{Results}
The experiment performed in \citet{spoton} showed that there were some problems with accuracy, but they were primarily caused by the imprecise tags used.
They had in mind to develop their own hardware in order to improve on this aspect.

\paragraph{Criticism}
This method of triangulation is dependent on the calibration of the model of each base station.
It is therefore prone to errors when the environment changes.
Moving the tag or even the surrounding objects will influence the precision of the calculations.

Also the hillclimbing method can be a problem in big buildings or big rooms, if there is no way to provide a good guess for the initial position.
Here short ranged RFID tags used for room partitioning could be used in order to have a reasonable starting point.

